---
title: " Mountain Crawler"
author: "Daniel Muzyka"
date: "3/28/2022"
output: html_document
---
# Crwaling up some Mountains' Stats

This program will crawl onthesnow.com to populate the mountain stats that I am too lazy to hand code into my data set because I want to act like a true Data Scientist.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("Rcrawler")
```

## Crawling

Coming soon!

This section will somehow use my existing data set to determine which webpages @ onthesnow.com contain the mountain stats I desire
```{r}

```


## Extracting from specific webpages

This section was my very first proof of concept that I can retrieve the information I want.

Success! Now I need to parse info so I can cleanly merge onto my existing data set.


```{r cars}
#Specify the Elements of the webpage that I would like to retrieve
Elements <- c(".styles_box__1sXJN", ".styles_box__1xP75", ".styles_box__1j4nK", ".styles_elevation__2L-EV", ".styles_box__1iaJy")

#Trying it out for Mammoth Mountain
mammoth <- ContentScraper(Url = "https://www.onthesnow.com/california/mammoth-mountain-ski-area/ski-resort",
CssPatterns = Elements, astext = TRUE)

mammoth

#Trying on Crystal Mountain. Are the elements the same on for each webpage? YES! That makes this easier.
crystal <- ContentScraper(Url = "https://www.onthesnow.com/washington/crystal-mountain-wa/ski-resort",
CssPatterns = Elements, astext = TRUE)

crystal
```
## Parsing info

Coming soon! It's 12pm and I have an interview tomorrow. Time to quit before I go too deep.

```{r}

```
